Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-08-15 batchdedup/analysis.tex
updates to performance model

We first analyze the time cost of 5 stages assuming an evenly distributed load
across the machines. Later we analyze the additional costs associated with an
imbalanced load.

In Stage 1, the dirty segments are read from the virtual disk, the hash of each
block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Since we must read $r$ blocks from disk, send
$r$ dedup requests, and then save the requests to temporary files (one for each
parition), the time for the first stage can be expressed as:
\[
    b_r r c + \alpha_n\frac{u r}{m_n} + b_w r u
\]

In Stage 2, each partition index is read from disk, then the dedup requests for
that paritition are processed and the results are written back out to disk to
be sent in Stage 3. The results are broken into 3 groups: duplicate blocks, new
blocks, and dup-with-new blocks, which are duplicates of blocks that are new to
this batch.

Let $n$ be the total number of index entries in the system.
$n=(p v x)(1-d_1)(1-d_2)\frac{e}{c}$,
which represents the index cost for all the deduped data in the system.
Since each machine holds a constant number $q$ paritions, and the paritions
should be uniform in size as they are from the hash of the block,
the total number of index entries at each machine should be $n/p$

The cost of Stage 2 is:
\[
    b_r r u + b_r\frac{n e}{p} + r \beta + b_w r e
\]

In Stage 3 the new block results from Stage 2 are sent to the requesters, and
in Stage 3b the new blocks are written out to the storage system. We will now
mostly be dealing with the $r(1-d_2)$ blocks that are new to the system. In 3b
the dedup results must be read and the actual disk blocks for each new block
must be re-read before they can be sent to the block store.

The cost of Stage 3 is:
\[
    b_r r(1-d_2)e + \alpha_n\frac{e r(1-d2)}{m_n} + b_w r(1-d_2)e
\]
and the cost of Stage 3b is:
\[
    b_r r(1-d_2)(e+c) + b_b r(1-d_2)c
\]

After the new blocks have been written to the block store, and references to
them have been obtained, those references must be returned to the parition
index holder so that those blocks may be deduped in the future. This Stage 4 (read the new index entries, return them to the parition master, and save the received references) costs:
\[
    b_r r (1-d_2)e + \alpha_n\frac{e r(1-d_2)}{m_n} + b_w r(1-d_2)e
\]

Stage 4b consists of updating the partition index with the new block references
from Stage 4, and costs:
\[
    b_r r (1-d_2)e + b_w r(1-d_2)e
\]

In the final stage (Stage 5), dup-with-new references are returned to the
requesters, so that the snapshot recipes may be updated with references to
those blocks. This process costs:
\[
    b_r r d_3 e + \alpha_n\frac{e r d_3}{m_n} + b_w r e
\]

Memory Requirments:\\
In every stage we need 1 disk read buffer, And then additionally we need the following:
\begin{description}
    \item[Stage 1] network buffers, and $q$ disk write buffers
    \item[Stage 2] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
    \item[Stage 3] network buffers, $v$ disk write buffers (for dedup responses)
    \item[Stage 3b] 1 disk write buffer (to write out new blocks)
    \item[Stage 4] network buffers, $q$ disk write buffers (to write out new refs)
    \item[Stage 4b] 1 disk write buffer (to update patition index with new blocks)
    \item[Stage 5] network buffers
\end{description}

>>>>

Define $r = s v (1-d_1)/(ck)$  which is the average number of detection
requests made by each machine, and the number of detection requests each
machine must handle.  We assume the load, i.e., amount of data to backup at
each machine, is not balanced, so there is also $r_max$, which is the number of
requests at the most heavily loaded machine. This is the case in the Alibaba
cluster, with some machines being terabytes while the average machine is 40GB.

Here we develop a model for the total backup time, which becomes important in
trying to minimize the CoW cost during backup \emph{CoW should be explained and
justified before this point in the paper}.  The backup process can be broken
into 4 stages, where each stage has two parts, first an all-to-all exchange of
data, then local processing to prepare for the next stage.

In Stage 1a, the dirty segments are read from the virtual disk, the hash of
each block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Due to the synchronization in each stage, Stage
1a needs to wait for the most heavily loaded machine to read all it's data - so
the read stage depends on $r_{max}$, while the write stage, which is balanced
by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
send $r$ dedup requests, and then save the received requests to temporary files
(one for each parition). The time for the first stage can be expressed as:
\[
    r_{max} c + \alpha_n\frac{u r_{max}}{m_n} / b_r + r u / b_w
\]

In Stage 1b, each partition index is read from disk, then the dedup requests
(from Stage 1a) for that paritition are processed and the results are written
back out to disk. The results are broken into 3 groups: duplicate blocks, new
blocks, and dup-with-new blocks, which are duplicates of blocks that are new to
this batch.

Let $n$ be the total number of index entries at each machine before the backup
was started.  $n=(v x)(1-d_1)(1-d_2)\frac{e}{c}$. Since each machine holds a
constant number $q$ paritions, and the paritions are uniform in size as they
are from the hash of the block, $n$ is very even across the machines, even when
the vm load is imbalanced.

The cost of Stage 1b is:
\[
    r u / b_r + (n e)b_r + r \beta + r e / b_w
\]

In Stage 2a the new block results from Stage 1 are sent to the requesters, and
in Stage 2b the new blocks are written out to the storage system. We will now
mostly be dealing with the $r(1-d_2)$ blocks that are new to the system (or
$r_{max}(1-d_2)$ when we must wait for the most heavily loaded machine). In 2b
the dedup results must be read and the actual disk blocks for each new block
must be re-read before they can be sent to the block store. The CoW locking on
the filesystem cannot end until after the dirty data is re-read in Stage 2b.

The cost of Stage 2a is:
\[
    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2)}{m_n} + r_{max}(1-d_2)e / b_w
\]
and the cost of Stage 2b is:
\[
    r_{max}(1-d_2)(e+c) / b_r + r(1-d_2)c / b_b
\]

After the new blocks have been written to the block store, and references to
them have been obtained, those references must be returned to the parition
index holder so that those blocks may be deduped in the future (and also so
dup-with-new requests can be handled in this run). This Stage 3a, to read the
new index entries, return them to the parition index holder, and save the
received references, costs:
\[
    r (1-d_2)e / b_r + \alpha_n\frac{e r(1-d_2)}{m_n} + r(1-d_2)e / b_w
\]

Stage 3b consists of updating the partition index with the new block references
from Stage 3a, and also updating the dup-with-new results from Stage 1. First
we load the new references from Stage 2b into memory, and then dedup the
dup-with-new requests against the new block references and save the dup-with
new requests back to disk. We then add the new references to the corresponding
partition index to handle future dedup requests. Stage 3b costs:
\[
    r (1-d_2)e / b_r + r(1-d_2)e / b_w
\]

In the final stage (Stage 4), dup-with-new references are returned to the
requesters, so that the snapshot recipes may be updated with references to
those blocks. This process costs:
\[
    r d_3 e / b_r + \alpha_n\frac{e r d_3}{m_n} + r e / b_w
\]

Memory Requirments:\\
In every stage we need 1 disk read buffer, And then additionally we need the following:
\begin{description}
    \item[Stage 1a] network buffers, and $q$ disk write buffers
    \item[Stage 1b] $n/q$ partition index space, and $p$ disk write buffers (for dedup responses)
    \item[Stage 2a] network buffers, $v$ disk write buffers (for dedup responses)
    \item[Stage 2b] 1 disk write buffer (to write out new blocks)
    \item[Stage 3a] network buffers, $q$ disk write buffers (to write out new refs)
    \item[Stage 3b] 1 disk write buffer (to update patition index with new blocks)
    \item[Stage 4] network buffers, $v$ disk write buffers
\end{description}
